---
title: "Simple but neat document"
author: Ravi Brenner
date: 2024-09-10
output: 
  github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

Loaded packages (e.g. `tidyverse`)

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Learning assessment

Learning assessment: Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

Here is the code, creates `my_df` and then plots a histogram

```{r histogram, message=FALSE}
# can create variable and immediately use it with the tibble function (if they're in order)
# with base R dataframe function, you can't do this
my_df <- tibble(
  num_var = rnorm(500, mean = 1),
  log_var = if_else(num_var > 0, TRUE, FALSE),
  num_var_abs = abs(num_var)
)

ggplot(my_df,aes(x = num_var_abs)) +
  geom_histogram()
```

The median value is `r round(median(my_df$num_var_abs),2)`

# Formatting text

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell